---
title: "GC-3 Workshop: Exercise"
author: "Yichi Zhang"
date: "2022-11-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here) 
library(haven)
library(lavaan)
library(tidyverse)
library(psych)
library(papaja)
## install package pinsearch if first time using this package
# install.packages("devtools")
# devtools::install_github("marklhc/pinsearch")
library(pinsearch)
```

In the demonstration, we investigated measurement invariance (MI) of the mini-IPIP across gender. Specifically, we focused on the subscale neuroticism. Please work on the subscale extraversion in this example. Good luck :) 

# Import Data
  
```{r}
data <- read.table(here::here("example", "IPIPFFM.dat"),
                   header = TRUE)%>%
  select("sex", "e1", "e4", "e6", "e7", "n1", "n2", "n6", "n8")
head(data)
```

# Model Specification

```{r}
mod_ex <- 'Extraversion =~ e1 + e4 + e6 + e7'
# original extraversion model
fit_e <- cfa(mod_ex, data = data)
summary(fit_e, fit.measures = TRUE)
```

```{r}
semPlot::semPaths(lavaanify(mod_ex), rotation = 2, intercepts = TRUE)
```

# Testing Metric Invariance

- Metric Invariance add equality constraints on factor loadings across groups

- The Likelihood Ratio Test (LRT) suggests the metric invariance model has similar fit as the configural invariance model

```{r}
# fit configural invariance model
fit_con <- cfa(mod_ex, data = data, group = "sex", std.lv = TRUE) 
summary(fit_con, fit.measures = TRUE)
# fit metric invariance model
fit_met <- cfa(mod_ex, data = data, group = "sex", group.equal = "loadings", std.lv = TRUE)
# summary(fit_met, fit.measures = TRUE)
lavTestLRT(fit_con, fit_met)
```

# Testing Scalar Invariance

- Scalar invariance add equality constraints on factor loadings and intercepts across groups

- The LRT suggests the scalar invariance model fit significantly worse than the metric invariance model

```{r}
# fit scalar invariance model
fit_sca <- cfa(mod_ex, data = data, group = "sex", 
               group.equal = c("loadings", "intercepts"), std.lv = TRUE) 
#summary(fit_sca, fit.measures = TRUE)
lavTestLRT(fit_sca, fit_met)
```

# Option 1: `pinSearch` Function From `pinsearch` Package

- This function automates the iterative search for noninvariant parameters 
(loadings, intercepts, residuals)

- item 6 has noninvariant intercepts across groups  

```{r}
res <- pinsearch::pinSearch(config_mod = mod_ex, data = data, effect_size = TRUE,
                     group = "sex",  type = "residuals")
res$`Non-Invariant Items`
res$effect_size
```

# Option 2: Sequential MI Testing By Scale Items

- Manually searching for noninvariant parameters (loadings, intercepts, residuals)

- Find the item associated with the largest change in $\chi^2$ => item e6

```{r}
# fit scalar invariance model
fit_sca1 <- cfa(mod_ex, data = data, group = "sex", 
                group.equal = c("loadings", "intercepts"), 
                group.partial = "e1 ~1", std.lv = TRUE) 
lavTestLRT(fit_sca1, fit_sca)
```

-----------------

```{r}
fit_sca4 <- cfa(mod_ex, data = data, group = "sex", 
                group.equal = c("loadings", "intercepts"), 
                group.partial = "e4 ~1", std.lv = TRUE) 
lavTestLRT(fit_sca4, fit_sca)
```


```{r}
fit_sca6 <- cfa(mod_ex, data = data, group = "sex", 
                group.equal = c("loadings", "intercepts"),
                group.partial = "e6 ~1", std.lv = TRUE) 
lavTestLRT(fit_sca6, fit_sca)
```

-----------------

```{r}
fit_sca7 <- cfa(mod_ex, data = data, group = "sex", 
                group.equal = c("loadings", "intercepts"),
                group.partial = "e7 ~1", std.lv = TRUE) 
lavTestLRT(fit_sca7, fit_sca)
```

```{r}
lavTestLRT(fit_sca6, fit_met)
```

# Testing Strict Invariance

- The partial strict invariance model has a similar fit to the partial scalar invariance model

- Conclusion: items `e1`, `e4`, `e7` are strict invariant, and item `e6` is weak invariant 

- Final model: partial strict invariance model with freely estimated intercept for item `e6`.

```{r}
fit_str <- cfa(mod_ex, data = data, group = "sex", 
                group.equal = c("loadings", "intercepts", "residuals"),
                group.partial = "e6 ~1", std.lv = TRUE) 
lavTestLRT(fit_sca6, fit_str)
```